Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
reflow, tidy

Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social associations
over long time periods 
represent shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home
range overlap is an example of how animals share space over coarser spatial and
temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of social interactions, such as social association and home range overlap, vary
predictably [@Castles_2014; @Farine_2015a]. 
We therefore define social scale as the explicit definition 
and measurement of social relationships [@Farine_2015a]. 
<!-- for QW:  -->
<!-- and suggest the potential for adaptive variance in social relationships is also scale-dependent.  -->
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->

@@

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). Multilayer networks consisted of the social 
associations between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers 
(foraging, forest and
open) for the entire study period. <!--TODO: check JWT / more clear to
remove this redundance already mentioned in net lay construction? 
Social associations of individuals were
defined by spatiotemporal overlap within 5 minutes and 50 m.--> For each 
land cover resolution, we calculated individual graph strength within each
habitat layer, and edge overlap and multidegree across habitat layers.

@@

Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]

@@

<!-- temp -->
<!-- TODO: results

-->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
We found increased edge overlap and graph strength in fall, winter and spring (approximately October - 
June) than in summer (approximately June - October) (Figure \@ref(fig:temp) A, C). 
These periods of increased sociality correspond 
to seasons of heterogeneous resource availability [Peigner_2019]. This analysis 
could be extended using time-aggregated networks and a
moving-window approach to time window size
and sampling effort [@Farine_2017; @Bonnell_2020]. By explicitly 
considering the temporal context of social interactions in separate layers, multilayer
networks provide a detailed and dynamic perspective of animal social networks.
For example, female mandrill (*Mandrillus sphinx*) sociality is more completely
represented by temporal multilayer networks than aggregated networks 
[@Pereira_2020]. Evans et al. [-@Evans_2020]
observed seasonal differences in the social structure of mice 
(*Mus musculus domesticus*) related to temperature and breeding activity. 
Finally, it is crucial to include sufficient data within sampling periods or time windows
to construct robust networks [@Farine_2017; Proskurnikov_2017]. With increasing
number of observations, we found
variance decreased in edge overlap and multidegree across habitat layers as well
as in graph strength within habitat layers (Figure \@ref(fig:nobs)). 
As more observations were added, rarer
relationships were recorded demonstrating the value of this form of sensitivity
analysis.

@@

Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018].

Incorporating
movement ecology within a multilayer network framework is a logical next step
for a burgeoning field. Importantly, the technological advancements in
biologging and wildlife tracking technology [@Borger_2020] have enabled this
unique opportunity to integrate movement and habitat in multilayer networks to
answer complex questions about animal socioecology.
-->

@@

<!-- TODO repeat qs-->

>>>>

Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social associations
over long time periods 
represent shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home
range overlap is an example of how animals share space over coarser spatial and
temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of social interactions, such as social association and home range overlap, vary
predictably [@Castles_2014; @Farine_2015a]. 
We therefore define social scale as the explicit definition 
and measurement of social relationships [@Farine_2015a].

@@

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). Multilayer networks consisted of the social
associations between `r DT[, uniqueN(get(idcol))]` individuals across three
habitat layers (foraging, forest and open) for the entire study period. For each
land cover resolution, we calculated individual graph strength within each
habitat layer, and edge overlap and multidegree across habitat layers.

@@

Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] 
us to confirm the use of 50 m buffer that has long been used
for studies in the field [@Lingle_2003; @Clutton_1982].

@@

<!-- temp -->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information.
We found increased edge overlap and graph strength in fall, winter and spring
(approximately October - June) than in summer (approximately June - October)
(Figure \@ref(fig:temp) A, C). These periods of increased sociality correspond
to seasons of heterogeneous resource availability [Peigner_2019]. This analysis
could be extended using time-aggregated networks and a moving-window approach to
time window size and sampling effort [@Farine_2017; @Bonnell_2020]. By
explicitly considering the temporal context of social interactions in separate
layers, multilayer networks provide a detailed and dynamic perspective of animal
social networks. For example, female mandrill (*Mandrillus sphinx*) sociality is
more completely represented by temporal multilayer networks than aggregated
networks [@Pereira_2020]. Evans et al. [-@Evans_2020] observed seasonal
differences in the social structure of mice (*Mus musculus domesticus*) related
to temperature and breeding activity. Finally, it is crucial to include
sufficient data within sampling periods or time windows to construct robust
networks [@Farine_2017; Proskurnikov_2017]. With increasing number of
observations, we found variance decreased in edge overlap and multidegree across
habitat layers as well as in graph strength within habitat layers (Figure
\@ref(fig:nobs)). As more observations were added, rarer relationships were
recorded demonstrating the value of this form of sensitivity analysis.
<!-- temp -->

@@

Integrating habitat-specific
movement layers could further illuminate the role of movement as a driver of the
social and spatial environments an individual experiences [@Webber_2018]. 
-->

@@
